### 2017-03-16 readme.Rmd
update readme

```{r}
po_v_lampra <- v_lampra[,c("longitude","latitude")]
tassie_preds_two <- stack(tassie_preds,(1-exp(p_bias_cell*-1)))
names(tassie_preds_two)[8] <- 'bias'

@@

```{r,fig.height=8,fig.width=12}
fm_v_lampra_w_s <- gam(presence/weights ~ s(annual_mean_temperature) +
                                      s(annual_precipitation) +
                                      s(max_temperature_of_warmest_month) +
                                      s(min_temperature_of_coldest_month) +
                                      s(precipitation_of_driest_month),
                                      offset=log(bias),
                                      weights = weights,
                                      data = bkpts_v_lampra,
                                      family = poisson())

@@

par(mfrow=c(1,2),oma=c(4,4,4,4))
plot(p_v_lampra_w_s_cell,col=jet.colors(100),main='accounting for sighting bias',
  xlim=c(144.5, 148.5), ylim=c(-43.8,-40.5))
points(po_v_lampra,pch=16,cex=0.4,col=rgb(0, 0, 0, 0.3))
plot(p_v_lampra_wo_s_cell,col=jet.colors(100),main='ignoring sighting bias',
  xlim=c(144.5, 148.5), ylim=c(-43.8,-40.5))
points(po_v_lampra,pch=16,cex=0.4,col=rgb(0, 0, 0, 0.3))

>>>>

```{r}
po_v_lampra <- v_lampra[,c("longitude","latitude")]
tassie_preds_two <- stack(tassie_preds,p_bias_cell)
names(tassie_preds_two)[8] <- 'bias'

@@

```{r,fig.height=8,fig.width=12}
fm_v_lampra_w_s <- gam(presence/weights ~ s(annual_mean_temperature) +
                                      s(annual_precipitation) +
                                      s(max_temperature_of_warmest_month) +
                                      s(min_temperature_of_coldest_month) +
                                      s(precipitation_of_driest_month),
                                      offset = log(bias),
                                      weights = weights,
                                      data = bkpts_v_lampra,
                                      family = poisson())

@@

brks <- seq(min(p_v_lampra_w_s_cell[],na.rm = TRUE),.5,length.out=100)
arg <- list(at=seq(0,.5,.05),labels=as.character(seq(0,.5,.05)))

par(mfrow=c(1,2),oma=c(4,4,4,4))
plot(p_v_lampra_w_s_cell,col=jet.colors(100),main='accounting for sighting bias',
  xlim=c(144.5, 148.5), ylim=c(-43.8,-40.5))#,breaks=brks,axis.args=arg)
points(po_v_lampra,pch=16,cex=0.4,col=rgb(0, 0, 0, 0.3))
plot(p_v_lampra_wo_s_cell,col=jet.colors(100),main='ignoring sighting bias',
  xlim=c(144.5, 148.5), ylim=c(-43.8,-40.5))
points(po_v_lampra,pch=16,cex=0.4,col=rgb(0, 0, 0, 0.3))
